\textbf{AprilTrack: A Particle-Filter based AprilTag Tracker}

### 2017-01-17 paper/paper.tex
Made quick fix to paper

\begin{figure*}[t]
	\label{fig:error}
	\includegraphics[width=\textwidth,height=9cm]{Average_Error}
	\caption{The average corner error between the hand-marked tag location and the tracked location. Much of the error from frames 0-200 comes from discrepancy between the tracker and the ground truth on the boundaries of blurred tags. At around frame 200, the tracker loses the tag due to a sudden rotation but is able to recover without needing a hard reset.}
\end{figure*}

>>>>

\begin{figure*}[t]
	\label{fig:error}
	\includegraphics[width=\textwidth,height=9cm]{Average_Error}
	\caption{The average corner error between the hand-marked tag location and the tracked location. Much of the error comes from discrepancy between the tracker and the ground truth on the boundaries of the blurred tags. At around frames 30 and 200, the tracker loses the tag momentarily due to a sudden rotation but is able to recover without needing to be manually reset.}
\end{figure*}
